Face Detection Based on Neural Network

### 2022-11-21 ML1/paper.tex
11-21-2

% Write abstract here
\begin{abstract}
abstract abstract abstract abstract
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is a important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619}

% Main Part
\section{Methods and Theory}
In this section, you are asked to give a complete introduction to the experiment. For instance, the chosen methods, the related theories, the related equations(loss function), the derivation process(taking the gradient) and so on.

\section{Experiments}
\subsection{Dataset}
This section represents the related information of datasets, such as the content, the number of data, the training set, the validation set and so on.

\subsection{Implementation}
All detailed implementation in your experiment: initialization, process, results, all kinds of parameters. In a word, describe clearly What you do and how you do.\par

	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot} and \ref{fig:13869}.

	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
	\begin{table}[!hbt]
		% Center the table
		\begin{center}
		% Title of the table
		\caption{Simulation Parameters}
		\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			Information message length & $k=16000$ bit \\
			\hline
			Radio segment size & $b=160$ bit \\
			\hline
			Rate of component codes & $R_{cc}=1/3$\\
			\hline
			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
			\hline
		\end{tabular}
		\end{center}
	\end{table}

@@

	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
	\begin{figure}[!hbt]
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{plot_tf}
		% Create a subtitle for the figure.
		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:tf_plot}
		\end{center}
	\end{figure}

		\begin{figure}[!hbt]
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/13869.jpg}
		% Create a subtitle for the figure.
		\caption{result with a person}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869}
		\end{center}
	\end{figure}

\section{Conclusion}
	This section summarizes the paper. In our experiments, you can also write your gains and inspirations in here.

>>>>

% Write abstract here
\begin{abstract}
This report is about first experience in machine learning. We explained how to build a anaconda environment to launch python scripts. In second part, three deep learning models to face detection was been used. Consequently, statistics of this experience was been showed and in the final, we have attached some face detection results.
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is a important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} used convolutional neural network (CNN). This experience use method raised by \cite{8080244} to detection faces in photos.

% Main Part
\section{Methods and Theory}
In \cite{8080244}, it propose Multi-task convolutional neural network

\section{Experiments}
\subsection{Dataset}
Test dataset includes handurds of photos and all of them has at least one people.

\subsection{Result}
We used the parameters archive files provided by Github repository to test truly effect of these three models. Program scripts load images from test photos folder, annotated them by face in and conveted annotated images into result folder. Whole test processing cost about 9 sec. by a laptop. We picked two of them to explain the effects of face detection, both of them have at least two person in it. First photo like Fig.\ref{fig:13869_raw} includes two persons, while one of them was back to the camera and another was frontal. So only face-to-camera one's face was been annotated by program like Fig.\ref{fig:13869}. Another photo that three person in was been annotated exactly with all the people like Fig.\ref{fig:13692}

	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
% 	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot} and \ref{fig:13869}.

	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
% 	\begin{table}[!hbt]
% 		% Center the table
% 		\begin{center}
% 		% Title of the table
% 		\caption{Simulation Parameters}
% 		\label{tab:simParameters}
% 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
% 		\begin{tabular}{|c|c|}
% 			% To create a horizontal line, type \hline
% 			\hline
% 			% To end a column type &
% 			% For a linebreak type \\
% 			Information message length & $k=16000$ bit \\
% 			\hline
% 			Radio segment size & $b=160$ bit \\
% 			\hline
% 			Rate of component codes & $R_{cc}=1/3$\\
% 			\hline
% 			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
% 			\hline
% 		\end{tabular}
% 		\end{center}
% 	\end{table}

@@

	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
% 	\begin{figure}[!hbt]
% 		% Center the figure.
% 		\begin{center}
% 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
% 		\includegraphics[width=\columnwidth]{plot_tf}
% 		% Create a subtitle for the figure.
% 		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
% 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
% 		\label{fig:tf_plot}
% 		\end{center}
% 	\end{figure}

		\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/13869.jpg}
		% Create a subtitle for the figure.
		\caption{result with a person}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869}
		\end{center}
	\end{figure}

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/13692.jpg}
		% Create a subtitle for the figure.
		\caption{result with three person}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692}
		\end{center}
	\end{figure}

	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13692.jpg}
		% Create a subtitle for the figure.
		\caption{three person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13692_raw}
		\end{center}
	\end{figure}
	\begin{figure}
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{images/img_13869.jpg}
		% Create a subtitle for the figure.
		\caption{two person in a photo}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:13869_raw}
		\end{center}
	\end{figure}

\section{Conclusion}
	Multi-task convolutional neural network can play a crucial role in face detection.
